Millions of Type Errors

### 2023-05-22 oopsla23/paper.tex
relabel tbl col

@@

  \begin{tabular}{lrrrr}
    & Local Remove & Local Add & Nonlocal Remove & Nonlocal Add \\
    Mode
    & \#err (count)
    & \#err (count)
    & \#err (count)
    & \#err (count) \\\midrule
    \mnocheck{}   & 86 (71) & 0 (0) & 110 (57) & 161 (74) \\
    \mnonstrict{} & 87 (25) & 9 (3) & 185 (29) & 207 (37) \\
    \mstrict{}    &  1  (1) & 0 (0) &  14  (6) &   6  (3) \\
  \end{tabular}

>>>>

FILL ignore sessions close to start / end time?
remove all syntax errors from later stages?

@@

  \begin{tabular}{lrrrr}
    & Local Remove & Local Add & Nonlocal Remove & Nonlocal Add \\
    Mode
    & \#err (\#log)
    & \#err (\#log)
    & \#err (\#log)
    & \#err (\#log) \\\midrule
    \mnocheck{}   & 86 (71) & 0 (0) & 110 (57) & 161 (74) \\
    \mnonstrict{} & 87 (25) & 9 (3) & 185 (29) & 207 (37) \\
    \mstrict{}    &  1  (1) & 0 (0) &  14  (6) &   6  (3) \\
  \end{tabular}
